\section*{START HERE: Instructions}
\begin{itemize}
    \item \textbf{Collaboration policy:} All are encouraged to work together BUT you must do your own work (code and write up). If you work with someone, please include their name in your write up and cite any code that has been discussed. If we find highly identical write-ups or code without proper accreditation of collaborators, we will take action according to university policies, i.e. you will likely fail the course. See the \href{https://www.dropbox.com/s/z6o0tinc9eaez46/L01_Overview.pdf?dl=0}{Academic Integrity Section} detailed in the initial lecture for more information.
          \item\textbf{Submitting your work:}
          \begin{itemize}
              \item We will be using Gradescope (\url{https://gradescope.com/}) to submit the Problem Sets. Please use the provided template. Submissions can be written in LaTeX, or submitted as a scanned PDF. Regrade requests can be made, however this gives the TA the opportunity to regrade your entire paper, meaning if additional mistakes are found then points will be deducted.
                    Each derivation/proof should be  completed on a separate page. For short answer questions you \textbf{should} include your work in your solution.
              \item For questions where you must fill in a blank, please make sure your final answer is fully included in the given space. You may cross out answers or parts of answers, but the final answer must still be within the given space. We accept either LaTex pdfs or scanned documents as long as the location of each question is annotated properly.

          \end{itemize}
    \item \textbf{Materials:} The data that you will need in order to complete this assignment is posted along with the writeup and template on Piazza.
\end{itemize}